Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
lower case

@@

The \nameref{sec:soa} section reviews recent research in the computational modeling of musical timbre.
The \nameref{sec:survey} section describes our data collection procedure for auditory similarities across playing techniques.
The \nameref{sec:method} section presents the technical components of our machine listening system, namely joint time--frequency scattering and large-margin nearest neighbors.
The \nameref{sec:results} section conducts an ablation study of our system.
The \nameref{sec:discussion} section summarizes the implications of our findings for future research on timbral similarity.\footnote{Reproducible research statement: the implementation of the proposed model and the experimental protocol of this paper are available online, alongside anonymized data from human subjects:  \url{https://github.com/mathieulagrange/paperPlayingTechniquesSimilarityLearning}} %TODO: simplify this URL to lostanlen2020jasmp

\section*{Related work}
\label{sec:soa}

@@

\section*{Proposed approach}
\label{sec:method}

@@

\section*{Timbre similarity judgments}
\label{sec:survey}

@@

To construct a dataset for exploring the perception of timbre, we conducted a survey on the perceived similarity of a set of sounds.
The set consists of $78$ recordings of different instrument--PT (IPT) pairs, each played at the same pitch (C4) and nuance \textit{mezzo forte}. For more information on the dataset considered in this study, see Section \ref{sec:appendix-dataset}.
In the survey, the subject is asked to organize dots on a two-dimensional place in a free sorting task.
Each dot corresponded to a different IPT recording and is moved by the user dragging them with the mouse.
In addition to spatially arranging the dots, the user is also asked to assign one of $20$ colors to each dot, providing a simple information of clustering of the sounds.
While both the location and color of each dot was recorded, only the color is used in our subsequent analysis---the spatial arrangement is only used to facilitate the user's ability to organize the sounds.
More information on the data collection process is available in  Section \ref{sec:subjective}.

@@

\section*{Results}
\label{sec:results}

@@

\section*{Discussion}
\label{sec:discussion}

@@

\section*{Competing interests}
  The authors declare that they have no competing interests.

\section*{Author's contributions}
    Text for this section \ldots

\section*{Acknowledgements}
The Flatiron Institute is a division of the Simons Foundation.

@@

% \section*{Dataset}
% \label{sec:appendix-dataset}
%
%
% The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of $16$ different musical instruments played with different PTs, which leads to $235$ different IPT pairs.
% In addition, the pitch and nuance is varie for each pair (when applicable), yielding a total of $25444$ audio recordings.
% For each couple, the pitch and intonation is varied leading to 25444 audio samples.
%
% The recorded instruments belongs to the wind and string classes.
% For winds, the instruments considered in the second experiment are: accordion (Acc), saxophone alto (ASax), tuba (Tb), bassoon (Bn), clarinet Bb (BbCl), flute (Fl), horn (Hn), oboe (Ob), trombone tenor (TTbn), and trumpet C (TpC).
% For the string class, the instruments are: guitar (Gtr), harp (Hp), viola (Va), violin (Vn), violoncello (Vc), and contrabass (Cb).
% \ml{Better to display these in a table? VL todo table}
%
% Those instruments are recorded for different nuance and pitch if the latter is relevant, but more importantly, several playing technique are considered.
% For the second experiment described in this paper, the playing techniques considered are: artificial harmonic (art), blow (blow), exploding slap (explo), harmonic (harm), key-click (key), col legno (legno), non vibrato (nonvib), ordinario (ord), pedal tone (pdl), pizzicato (pizz), ponticello (pont), slap (slap), (tasto), tongue-ram (tng), and xylophonic (xyl).
%
% \vl{This section is not precise enough in terms of intensity ranges and pitch ranges.
% The abbreviations can be removed. @data @writing}
% \ml{}
%
% \vl{A bubble plot of number of notes per instrument (x axis) and playing technique
% (y axis) would be extremely useful. @data @figure}
% \ml{Tu voudrais ca pour la base SOL complete ou les données considérées dans l'étude ?}
% \vl{Les donn\'{e} de l'\'{e}tude, relatives aux Figures 5 et 6.}

\section*{Human timbre judgments}
\label{sec:subjective}

@@

\section*{Reducing Expert judgments of technique peculiarities}

@@

%%%%%%%%%%%%%% CROWDSOURCED JUDGMENTS OF PAIRWISE SIMILARITY %%%%%%%%%%%%%%%%%%%%
\section*{Crowdsourced judgments of pairwise similarity}

>>>>

\newcommand{\lnameref}[1]{%
\bgroup
\let\nmu\MakeLowercase
\nameref{#1}\egroup}
\newcommand{\fnameref}[1]{%
\bgroup
\def\nmu{\let\nmu\MakeLowercase}%
\nameref{#1}\egroup}

\newcommand{\nmu}{}

@@

The \lnameref{sec:soa} section reviews recent research in the computational modeling of musical timbre.
The \lnameref{sec:survey} section describes our data collection procedure for auditory similarities across playing techniques.
The \lnameref{sec:method} section presents the technical components of our machine listening system, namely joint time--frequency scattering and large-margin nearest neighbors.
The \lnameref{sec:results} section conducts an ablation study of our system.
The \lnameref{sec:discussion} section summarizes the implications of our findings for future research on timbral similarity.\footnote{Reproducible research statement: the implementation of the proposed model and the experimental protocol of this paper are available online, alongside anonymized data from human subjects:  \url{https://github.com/mathieulagrange/paperPlayingTechniquesSimilarityLearning}} %TODO: simplify this URL to lostanlen2020jasmp

\section*{\nmu Related work}
\label{sec:soa}

@@

\section*{\nmu Proposed approach}
\label{sec:method}

@@

\section*{\nmu Timbre similarity judgments}
\label{sec:survey}

@@

To construct a dataset for exploring the perception of timbre, we conducted a survey on the perceived similarity of a set of sounds.
The set consists of $78$ recordings of different instrument--PT (IPT) pairs, each played at the same pitch (C4) and nuance \textit{mezzo forte}. For more information on the dataset considered in this study, see Section \ref{sec:subjective}.
In the survey, the subject is asked to organize dots on a two-dimensional place in a free sorting task.
Each dot corresponded to a different IPT recording and is moved by the user dragging them with the mouse.
In addition to spatially arranging the dots, the user is also asked to assign one of $20$ colors to each dot, providing a simple information of clustering of the sounds.
While both the location and color of each dot was recorded, only the color is used in our subsequent analysis---the spatial arrangement is only used to facilitate the user's ability to organize the sounds.
%More information on the data collection process is available in  Section \ref{sec:subjective}.

@@

\section*{\nmu Results}
\label{sec:results}

@@

\section*{\nmu Discussion}
\label{sec:discussion}

@@

\section*{\nmu Competing interests}
  The authors declare that they have no competing interests.

\section*{\nmu Author's contributions}
    Text for this section \ldots

\section*{\nmu Acknowledgements}
The Flatiron Institute is a division of the Simons Foundation.

@@

% \section*{\nmu Dataset}
% \label{sec:appendix-dataset}
%
%
% The dataset considered in this paper as been recorded at Ircam and is composed of audio recording of $16$ different musical instruments played with different PTs, which leads to $235$ different IPT pairs.
% In addition, the pitch and nuance is varie for each pair (when applicable), yielding a total of $25444$ audio recordings.
% For each couple, the pitch and intonation is varied leading to 25444 audio samples.
%
% The recorded instruments belongs to the wind and string classes.
% For winds, the instruments considered in the second experiment are: accordion (Acc), saxophone alto (ASax), tuba (Tb), bassoon (Bn), clarinet Bb (BbCl), flute (Fl), horn (Hn), oboe (Ob), trombone tenor (TTbn), and trumpet C (TpC).
% For the string class, the instruments are: guitar (Gtr), harp (Hp), viola (Va), violin (Vn), violoncello (Vc), and contrabass (Cb).
% \ml{Better to display these in a table? VL todo table}
%
% Those instruments are recorded for different nuance and pitch if the latter is relevant, but more importantly, several playing technique are considered.
% For the second experiment described in this paper, the playing techniques considered are: artificial harmonic (art), blow (blow), exploding slap (explo), harmonic (harm), key-click (key), col legno (legno), non vibrato (nonvib), ordinario (ord), pedal tone (pdl), pizzicato (pizz), ponticello (pont), slap (slap), (tasto), tongue-ram (tng), and xylophonic (xyl).
%
% \vl{This section is not precise enough in terms of intensity ranges and pitch ranges.
% The abbreviations can be removed. @data @writing}
% \ml{}
%
% \vl{A bubble plot of number of notes per instrument (x axis) and playing technique
% (y axis) would be extremely useful. @data @figure}
% \ml{Tu voudrais ca pour la base SOL complete ou les données considérées dans l'étude ?}
% \vl{Les donn\'{e} de l'\'{e}tude, relatives aux Figures 5 et 6.}

\section*{\nmu Human timbre judgments}
\label{sec:subjective}

@@

\section*{\nmu Reducing Expert judgments of technique peculiarities}

@@

%%%%%%%%%%%%%% CROWDSOURCED JUDGMENTS OF PAIRWISE SIMILARITY %%%%%%%%%%%%%%%%%%%%
\section*{\nmu Crowdsourced judgments of pairwise similarity}
